---
title: "Project Proposal for Team 07-7"
authors: "Amanda Cai, James Gao, Conor West"
output: pdf_document
editor_options:
  chunk_output_type: console
---


```{r global_options, include = FALSE}
knitr::opts_chunk$set(fig.align = "center",
                      fig.width = 3)
library(tidyverse)
library(infer)
``` 
 
# Data

## Dataset 1: NCAA Women's basketball

```{r load-bball}
bball <- read.csv("data/ncaa-womens-basketball-tournament-history.csv")
glimpse(bball)
```

For this dataset, our research question is "How strongly do conference tournament records and conference tournament wins correlate with NCAA tournament success as compared to overall regular season records?" Some additional/alternative questions might be, "Is home-court advantage stronger for certain teams and conferences? Which conferences outperform and underperform their seeds the most?"

Our hypothesis: Conference records will correlate more strongly with tournament success for Power 5 conference universities, but conference and regular season records will be equally predictive for all other schools. (If that's too complicated: Conference and regular season records will correlate equally.)

## Dataset 2: Super Bowl Ads

```{r load-super-bowl}
ads <- read.csv("data/superbowl-ads.csv")
glimpse(ads)
```

For this dataset, our research question is "What is the correlation between the
content of the advertisement and its corresponding success on YouTube? i.e. what
are the most important factors in determining Superbowl advertisement success?" 
Some alternative questions could be "Does sex actually sell? How important is 
the centrality of the product in the ad? How important are youtube interactions 
(likes, comments, etc.)?"

Our hypothesis: The best/most successful advertisements will be able to tell a 
compelling narrative while also keeping a wide variety of audiences entertained
and invested. The actual product itself will be less important than the humor,
sexuality, animals, etc. used.

## Dataset 3: Taylor Swift and Beyoncé Lyrics

```{r load-lyrics}
swift_lyrics <- read.csv("data/taylor_swift_lyrics.csv")
bey_lyrics <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-09-29/beyonce_lyrics.csv')
glimpse(swift_lyrics)
glimpse(bey_lyrics)

```

Source of the data: Taylor Swift’s Songs

How it was collected: Getting all the lyrics of her songs

The cases: The sentiments and emotions of the lyrics

Relevant variables: Artist, album, track title, track number, lyric, line, year

For this dataset, we are analyzing Beyonce’s lyrics based on the model by Rosie 
Baillie and Taylor Swift lyrics. The research question is “What emotions or 
sentiments are most present in each of Beyonce’s studio albums?”

Our hypothesis: The more recent albums will have more positive emotions and
sentiments (as compared to the older ones).